---
title: "Weight of Fish"
author: "Alondra Cruz"
date: "July 31st 2023"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
---

 setwd("C:/Users/16617/Documents/AVC/Math115/WUP_09")

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```

# Predicting Fish Weight
## get data
```{r}
fishData=read.csv("Fish.csv")
```


## Perch
```{r}
perch = filter(fishData, Species == "Perch")
```

### Best Models
```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=perch,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```
The best two variables to predict weight is height and width. 

### Best Two regressor model
The best two regressor models are
```{r}
perchModel=lm(Weight~Height+Width,data=perch)
summary(perchModel)
```
For the best model adjusted r square is 0.94


## Pike
```{r}
pike = filter(fishData, Species == "Pike")
```

### Best Models
```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=pike,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```
The best two variables for pike is Length 1 and Length 3. 

### Best Two regressor model
```{r}
pikeModel=lm(Weight~Length1+Length3,data=pike)
summary(pikeModel)
```
For the best model adjusted r square is 0.9649 

## Roach
```{r}
Roach = filter(fishData, Species == "Roach")
```

### Best Models
```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=Roach,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```
The best two variables for Roach is Length 3 and Width. 

### Best Two regressor model
```{r}
RoachModel=lm(Weight~Length3+Width,data=Roach)
summary(RoachModel)
```
For the best model adjusted r square is 0.8482


## Final Summary Statements